---
title: "GoGoGadget_An_Introduction"
author: "Zachary Thompson"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
vignette: >
  %\VignetteIndexEntry{Introduction_to_MoffittFunctions}
  %\VignetteEngine{knitr::rmarkdown} 
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
 #library(gogogadget)
```



# Overview

Gogogadget is a collection of useful functions designed to assist in analysis. 
 
- Functions
  gogogadgetexport
  gogofindvar
  gogostr
  
- Example Dataset
  - Bladder_Cancer


## Getting Started

```{r 2, echo=TRUE, message=FALSE, results='hide'}
# Loading MoffittFunctions and Example Dataset
 library(MoffittFunctions)
 data("Bladder_Cancer")

# Loading dplyr for this vignette code
library(dplyr)
```


## Example Dataset

The `Bladder_Cancer` dataset is a real world example dataset used throughout this vignette and most example in the documentation. The dataset is cleaned, using factor variables for categorical variables, and also using labels for all variables (created by the `Hmisc::label()` function).

```{r 3, echo=TRUE, message=FALSE, results='hide'}
 
str("Bladder_Cancer")
 
```

